Hydra Battles and Cie

### 2021-06-30 doc/chapter-primrec.tex
correction of typos
-  Corrections in latex files -  Export distributivity and associativity properties to type E0 -  minor changes (order of lemmas)
Fix pdf links (#41)

The constructors \texttt{zeroFunc}, \texttt{succFunc},  and \texttt{projFunc} of type
\texttt{PrimRec} allows us to write trivial proofs of primitive recursivity. 
Although  the following lemmas are already proven in 
\href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec.v},
we wrote alternate proofs in 
\href{../theories/html/hydras.MoreAck.PrimRecExamples.html}%
{Ackermann.MoreAck.PrimRecExamples.v}, in order to illustrate the main proof patterns.

@@

Projections are proved primitive recursive, case by case (many examples in 
\href{../theories/html/hydras.primRec.html}{Ackermann.primRec.v}).
\emph{Please notice again that the name of the projection follows the mathematical tradition, 
whilst the arguments of  \texttt{projFunc} use another convention (\emph{cf} remark~\vref{projFunc-order-of-args}).}

@@

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.primRec.html}{Ackermann.primRec}.}

@@

The lemma \texttt{plusIsPR} is already proven in \href{../theories/html/hydras.primRec.html}{Ackermann.primRec}. We present in 
\href{../theories/html/hydras.MoreAck.PrimRecExamples.html}{MoreAck.PrimRecExamples}
a commented version of this proof,

@@

\textbf{Hint:} You may have to look again at the lemmas of the library
\href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec} if you meet some difficulty.
You may start this exercise with the file
\url{../exercises/primrec/MorePRExamples.v}.
\end{exercise}

@@

\emph{You may start this exercise with
\url{../exercises/primrec/MinPR.v}.}

@@

\textbf{Hint:}  You may use as a helper the function which computes the pair \linebreak
$(\texttt{fib}(n+1),\texttt{fib}(n))$. 
Library \href{../theories/html/hydras.Ackermann.cPair.html}{Ackermann.cPair} contains
the definition of the encoding of $\mathbb{N}^2$ into $\mathbb{N}$, and the proofs that 
the associated constructor and projections are primitive recursive.
\emph{You may start this exercise with the file
\url{../exercises/primrec/FibonacciPR.v}.}

@@

\emph{You may start this exercise with the file
\url{../exercises/primrec/isqrt.v}.}

@@

Lemma Ack_S_0 m : Ack (S m) 0 = Ack m 1. 
Proof. now cbn. Qed.

Lemma Ack_S_S : forall m p,
    Ack (S m) (S p) = Ack m (Ack (S m) p).
Proof. now cbn. Qed.
\end{Coqsrc}

@@

We prove also a strict version of this lemma, thanks to the following property (proved in Library\href{../theories/html/hydras.MoreAck.Ack.html}{MoreAck.Ack}~).

@@

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.MoreAck.AcknotPR.html}{MoreAck.AckNotPR}.}

@@

\section{The length of standard hydra battles}

@@

Looking for lemmas of the form $H'_\beta(k)\leq H'_\alpha(k)$, we find this one (from our library
\href{../theories/html/hydras.Epsilon0.Hprimehtml}{Epsilon0.Hprime}):

@@

 Remark SmNotPR : isPR 1 (fun n => S (m n)) -> False.

>>>>

The constructors \texttt{zeroFunc}, \texttt{succFunc},  and \texttt{projFunc} of type
\texttt{PrimRec} allows us to write trivial proofs of primitive recursivity. 
Although  the following lemmas are already proven in 
\href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec},
we wrote alternate proofs in 
\href{../theories/html/hydras.MoreAck.PrimRecExamples.html}%
{Ackermann.MoreAck.PrimRecExamples.v}, in order to illustrate the main proof patterns.

@@

Projections are proved primitive recursive, case by case (many examples in 
\href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}).
\emph{Please notice again that the name of the projection follows the mathematical tradition, 
whilst the arguments of  \texttt{projFunc} use another convention (\emph{cf} remark~\vref{projFunc-order-of-args}).}

@@

@@

The lemma \texttt{plusIsPR} is already proven in \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}. We present in 
\href{../theories/html/hydras.MoreAck.PrimRecExamples.html}{MoreAck.PrimRecExamples}
a commented version of this proof,

@@

\textbf{Hint:} You may have to look again at the lemmas of the library
\href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec} if you meet some difficulty.
You may start this exercise with the file
    \href{https://https://github.com/coq-community/hydra-battles/blob/master/exercises/primrec/MorePRExamples.v}{exercises/primrec/MorePRExamples.v}.
\end{exercise}

@@

\emph{You may start this exercise with
    \href{https://https://github.com/coq-community/hydra-battles/blob/master/exercises/primrec/MinPR.v}{exercises/primrec/MinPR.v}.}

@@

\textbf{Hint:}  You may use as a helper the function which computes the pair \linebreak
$(\texttt{fib}(n+1),\texttt{fib}(n))$. 
Library \href{../theories/html/hydras.Ackermann.cPair.html}{Ackermann.cPair} contains
the definition of the encoding of $\mathbb{N}^2$ into $\mathbb{N}$, and the proofs that 
the associated constructor and projections are primitive recursive.
\emph{You may start this exercise with the file
    \href{https://github.com/coq-community/hydra-battles/blob/master/exercises/primrec/FibonacciPR.v}{exercises/primrec/FibonacciPR.v}.}

@@

\emph{You may start this exercise with the file
    \href{https://github.com/coq-community/hydra-battles/blob/master/exercises/primrec/isqrt.v}{exercises/primrec/isqrt.v}.}

@@

Lemma Ack_S_0 m : Ack (S m) 0 = Ack m 1. 
Proof. reflexivity. Qed.

Lemma Ack_S_S : forall m p,
    Ack (S m) (S p) = Ack m (Ack (S m) p).
Proof. reflexivity. Qed.
\end{Coqsrc}

@@

We prove also a strict version of this lemma, thanks to the following property (proved in Library
\href{../theories/html/hydras.MoreAck.Ack.html}{MoreAck.Ack}~).

@@

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.MoreAck.AckNotPR.html}{MoreAck.AckNotPR}.}

@@

\section{The length of standard hydra battles}
\label{sect:battle-length-notPR}

@@

Looking for lemmas of the form $H'_\beta(k)\leq H'_\alpha(k)$, we find this one (from our library
\href{../theories/html/hydras.Epsilon0.Hprime.html}{Epsilon0.Hprime}):

@@

Remark SmNotPR : isPR 1 (fun n => S (m n)) -> False.
(* ... *)
